### 2024-05-08 thesis/chapters/appendix/C-user-guide.tex
Generate doxygen docs and prepare Sphinx

\item {
Connect ESP32 microcontroller via USB and flash firmware onto the device:
\begin{lstlisting}[style=messages]
$ . ~/esp/esp-idf/esp-idf/export.sh
$ cd firmware
$ idf.py build
$ idf.py -p /dev/ttyUSB0 flash
\end{lstlisting}}

\end{enumerate}

@@

>>>>

\item {
Connect ESP32 microcontroller via USB and flash firmware onto the device:
\begin{lstlisting}[style=messages]
$ . ~/esp/esp-idf/esp-idf/export.sh
$ cd firmware
$ idf.py build
$ idf.py -p /dev/ttyUSB0 flash
\end{lstlisting}}
\end{enumerate}

@@

\section{Documentation guide}
Built documentation is located in directory \emph{docs} of digital medium. It can be rebuild using documentation tools \emph{Doxygen} for firmware C source code and \emph{Sphinx} for data analysis Python code. The steps of generating documentation from souce codes are as follows:

\begin{enumerate}[noitemsep]
\item {install necessary documentation tools:
\begin{lstlisting}[style=messages]
$ sudo pacman -S doxygen
$ pip install sphinx
\end{lstlisting}}
\item {rebuild the documentation using Doxygen and Sphinx:
\begin{lstlisting}[style=messages]
$ doxygen docs/firmware/doxygen.conf
$ cd docs/vibrodiagnostics
$ make html
\end{lstlisting}}
\item {View Doxygen docs in \emph{docs/firmware/html/topics.html} and Sphinx docs in \emph{docs/vibrodiagnostics/build/html/index.html}}
\end{enumerate}
